On Misuses of the Kolmogorov–Smirnov-Test

### 2022-04-22 Manuscript/manuscript.tex
updated introduction and non-parametric sections

\title{Survey of Misuses of the Kolmogorov–Smirnov-Test}

\author{Anthony Zeimbekakis and Jun Yan\\
\href{mailto:anthony.zeimbekakis@uconn.edu}{\nolinkurl{anthony.zeimbekakis@uconn.edu}}\\
Department of Statistics, University of Connecticut}
\date{January 23, 2021}

@@

\begin{abstract}
The Kolmogorov-Smirnov (K-S) test is one the most popular goodness-of-fit tests for 
comparing a sample with a hypothesized parametric distribution. Nevertheless, it has 
often been misused. The standard one-sample KS test applies to independent, continuous 
data with a hypothesized distribution that is completely specified. It is not uncommon, 
however, to see in the literature that it was applied to dependent, discrete, or 
rounded data, with hypothesized distributions containing estimated parameters. 
For example, it has been “discovered” multiple times that the test is too conservative 
when the parameters are estimated. This paper aims to survey the misuses of the KS test, 
demonstrate their consequences through simulation, and provide remedies as needed.
\end{abstract}

@@

The Kolmogorov-Smirnov (K-S) statistic is one of the most popular goodness-of-fit 
tests for comparing a sample with a hypothesized parametric distribution. The test is 
performed as follows. Given a sample of n observations, let $S_{n}(x)$ be the empirical 
cumulative distribution and $F(x)$ be the population cumulative distribution. The K-S 
statistic is defined by: \[d = max(\lvert F(x)-S_{n}(x) \rvert)\] The null hypothesis 
is that the observations are from the specified distribution $F(x)$, and the 
alternate hypothesis is that the data is not from $F(x)$. The table of critical 
values for $d$ are given by \citet{Massey} for various sample sizes $n$ and significance 
levels $a$. If the value of $d$ exceeds the test's corresponding critical value, 
the null hypothesis is rejected.

However, the test is often misused. The standard one-sample K-S test applies to 
independent, continuous data with a hypothesized distribution that is completely specified. 
Often in literature, it has been "discovered" that the test loses its power when 
applied to dependent or discrete data with hypothesized distributions containing 
estimated parameters. In the case of estimated parameters, \citet{Steinskog} 
demonstrates the change in power when using estimated parameters and stress caution in 
using the K-S test in such ways. \citet{Lilliefors} shows 
that using the standard table when values of the mean and standard deviation are 
estimated obtains extremely conservative results. This is supported by \citet{Capasso}, which 
concludes that failing to re-estimate the parameters may lead to wrong, overly-conservative 
approximations to the distributions of goodness-of-fit test statistics based on the empirical 
distribution function. \citet{Capasso} also notes that the impact of this possible mistake 
may turn out to be dramatic and does not vanish as the sample size increases. Remedies are provided 
by \citet{Genest} and \citet{Babu} in the form of bootstrap. \citet{Genest} provides validity 
for using parametric bootstrap with various goodness-of-fit tests. \citet{Babu} details 
the bootstrap procedure for goodness-of-fit tests and notes that both parametric and 
non-parametric procedures lead to correct asymptotic levels, however there is a correction 
required for the non-parametric case. In the case of dependent data, \citet{Durilleul} demonstrates 
that the K-S statistic is too liberal for medium-to-high positive autocorrelation values. 
\citet{Durilleul} also shows that for negative autocorrelation values, the behavior is 
asymmettrical with respect to positive values. For remedies, \citet{Weiss} provides a 
procedure that is applicable specifically for data modeled by the second-order auto-regressive (AR) process 
where the parameters are known. \citet{Lanzante} tests various strategies for dealing with temporal dependence
and concludes that a test based on Monte-Carlo simulations performed the best.
We propose a procedure involving copulas to account for dependence.

@@

\begin{itemize}
  \item 
    Let $X_1^*,...,X_n^*$ be i.i.d random variables from $\hat{S}_n$, an estimator 
    of the distribution function $S_n$ based on the sample $X_1,...,X_n$
  \item 
    Let $\hat{\theta}_n^* = \theta_n(X_1^*,...,X_n^*)$, where $\theta$ is the 
    parameter vector and $\hat{\theta}_n$ represents the sample mean and variance 
    of the sample $X_1,...,X_n$
  \item 
    $\hat{\theta}_n^*$ represents the sample mean and variance of the bootstrap 
    sample $X_1^*,...,X_n^*$
  \item Thus, the K-S statistic for each bootstrap case is $max(\lvert F(x)-S^*_n(x) \rvert)$
\end{itemize}

In parametric bootstrap, the resampling is done where $\hat{S}_n = F(.;\hat{\theta}_n)$. 
Bootstrap samples are drawn from ${F}(.,\hat{\theta}_n)$ where the assumed distribution 
$F$ is normal and $\hat{\theta}_n = (\Xbar, s)$, the sample mean and sample standard 
deviation. For each bootstrap sample, a K-S test statistic is found using those 
fitted parameters.

In non-parametric bootstrap, the resampling is done where $\hat{S}_n = S_n$.

@@

>>>>

\title{On Misuses of the Kolmogorov–Smirnov-Test}

\author{Anthony Zeimbekakis and Jun Yan\\
\href{mailto:anthony.zeimbekakis@uconn.edu}{\nolinkurl{anthony.zeimbekakis@uconn.edu}}\\
Department of Statistics, University of Connecticut}
\date{April 21, 2022}

@@

\begin{abstract}
The Kolmogorov-Smirnov (K-S) test is one the most popular goodness-of-fit tests for 
comparing a sample with a hypothesized parametric distribution. Nevertheless, it has 
often been misused. The standard one-sample KS test applies to independent, continuous 
data with a hypothesized distribution that is completely specified. It is not uncommon, 
however, to see in the literature that it was applied to dependent, discrete, or 
rounded data, with hypothesized distributions containing estimated parameters. 
For example, it has been “discovered” multiple times that the test is too conservative 
when the parameters are estimated. This paper aims to discuss misuses of the KS test, 
demonstrate their consequences through simulation, and provide remedies as needed.
\end{abstract}

@@

The Kolmogorov-Smirnov (K-S) statistic is one of the most popular goodness-of-fit 
tests for comparing a sample with a hypothesized parametric distribution. The test is 
performed as follows. Let $X_1, ..., X_n$ be i.i.d. random variables from $F_{n}(x)$,
the empirical cumulative distribution.
Let $F(x)$ be the population cumulative distribution. The K-S 
statistic is \[d = \max\lvert F_{n}(x) - F(x) \rvert\]. The null hypothesis 
is that the observations $X_1, ..., X_n$ are from the specified distribution $F(x)$, and the 
alternate hypothesis is that the data is not from $F(x)$. The table of critical 
values for $d$ are given by \citet{Massey} for various sample sizes $n$ and significance 
levels $a$. If the value of $d$ exceeds the test's corresponding critical value, 
the null hypothesis is rejected.

However, the test is often misused. The standard one-sample K-S test applies to 
independent, continuous data with a hypothesized distribution that is completely specified. 
Often in literature, it has been "discovered" that the test loses its power when 
applied to dependent or discrete data with hypothesized distributions containing 
estimated parameters. In the case of estimated parameters, \citet{Steinskog} 
demonstrates the change in power when using estimated parameters and stress caution in 
using the K-S test in such ways. \citet{Lilliefors} shows 
that using the standard table when values of the mean and standard deviation are 
estimated obtains extremely conservative results. This is supported by \citet{Capasso}, which 
concludes that failing to re-estimate the parameters may lead to wrong, overly-conservative 
approximations to the distributions of goodness-of-fit test statistics based on the empirical 
distribution function. \citet{Capasso} also notes that the impact of this possible mistake 
may turn out to be dramatic and does not vanish as the sample size increases. Remedies are provided 
by \citet{Genest} and \citet{Babu} in the form of bootstrap. \citet{Genest} provides validity 
for using parametric bootstrap with various goodness-of-fit tests. \citet{Babu} details 
the bootstrap procedure for goodness-of-fit tests and notes that both parametric and 
non-parametric procedures lead to correct asymptotic levels, however there is a correction 
required for the non-parametric case. In the case of dependent data, \citet{Durilleul} demonstrates
that the K-S statistic is too liberal for medium-to-high positive autocorrelation values. 
\citet{Durilleul} also shows that for negative autocorrelation values, the behavior is 
asymmettrical with respect to positive values. For remedies, \citet{Weiss} provides a 
procedure that is applicable specifically for data modeled by the second-order auto-regressive (AR) process where the parameters are known. \citet{Lanzante} tests various strategies for dealing with temporal dependenceand concludes that a test based on Monte-Carlo simulations performed the best.
We propose a bootstrap procedure involving copulas to account for dependence.

@@

\begin{itemize}
  \item 
    Let $X_1^*,...,X_n^*$ be i.i.d random variables from $\hat{F}_n$, an estimator 
    of the distribution function $F_n$ based on the sample $X_1,...,X_n$
  \item 
    Let $\hat{\theta}_n^* = \theta_n(X_1^*,...,X_n^*)$, where $\theta$ is the 
    parameter vector and $\hat{\theta}_n$ represents the sample mean and variance 
    of the sample $X_1,...,X_n$
  \item 
    $\hat{\theta}_n^*$ represents the sample mean and variance of the bootstrap 
    sample $X_1^*,...,X_n^*$
  \item Thus, the K-S statistic for each bootstrap case is $max(\lvert F(x)-F^*_n(x) \rvert)$
\end{itemize}

In parametric bootstrap, the resampling is done where $\hat{F}_n = F(.;\hat{\theta}_n)$. 
Bootstrap samples are drawn from ${F}(.,\hat{\theta}_n)$ where the assumed distribution 
$F$ is normal and $\hat{\theta}_n = (\Xbar, s)$, the sample mean and sample standard 
deviation. For each bootstrap sample, a K-S test statistic is found using those 
fitted parameters.

In non-parametric bootstrap, the resampling is done where $\hat{F}_n = F_n$. The non-parametric
case requires a correction for bias detailed by \citet{Babu}. There is a known bias
term $B_{n}(x) = \sqrt{n}(F_{n}(x) - F(x;\hat{\theta}_n)$. Including this term in the
calculation of the K-S statistic corrects the bias \citet{Babu}:
$d = \max\lvert F_{n}(x) - F(x) - B_{n}(x) \rvert$.

@@

\begin{figure}[tbp]
  \centering
  \includegraphics{hist_copula_ar2}
  \caption{Histograms demonstrating copula use to correct dependence.}
  \label{fig:hist_copula_ar2}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics{hist_copula_gev}
  \caption{Histograms demonstrating copula use to correct dependence.}
  \label{fig:hist_copula_gev}
\end{figure}
